Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-13 manuscript/manuscript.Rmd
Manuscript revision.

-   We define an empirical central normality test for detecting cases where power transformations fail to yield a roughly normally distributed transformed feature.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-shift}
\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left(\frac{x_i - x_0}{s} \right)^\lambda - 1 \right) / \lambda & \text{if } \lambda \neq 0\\
\log\left[\frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0
\end{cases}
\end{equation}
```

Where $x_i - x_0 > 0$. Likewise, the shift and scale invariant Yeo-Johnson transformation of a feature value $x_i$ under transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$ is:

@@

```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{BC}}^{\lambda, x_0, s} = & -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0} (\mathbf{X})$, respectively. Similarly, for the invariant Yeo-Johnson log-likelihood function is:
HEREHEHEHHRHEHHEHEHRER
```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-shift-log-likelihood}
\left\{ \hat{\lambda}^{\text{YJ}}, \hat{x}_0^{\text{YJ}} \right\} = \argmax_{\lambda, x_0} \sum_{i=1}^n -\frac{1}{2}\log(\sigma^2) + (\lambda - 1) \sgn(x_i - x_0) \log(1 + |x_i - x_0|)
\end{equation}
```
where $\sigma^2$ is the variance of Yeo-Johnson transformed feature $\phi_{\text{YJ}}^{\lambda, x_0} (\mathbf{X})$.

>>>>

-   We define an empirical central normality test for detecting cases where power transformations fail to yield an approximately normally distributed transformed feature.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-shift}
\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left(\frac{x_i - x_0}{s} \right)^\lambda - 1 \right) / \lambda & \text{if } \lambda \neq 0\\
\log\left[\frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0
\end{cases}
\end{equation}
```
where $x_i - x_0 > 0$. Likewise, the shift and scale invariant Yeo-Johnson transformation of a feature value $x_i$ under transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$ is:

@@

```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{BC}}^{\lambda, x_0, s} = & -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$, respectively. Similarly, for the invariant Yeo-Johnson log-likelihood function is:

```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-shift-log-likelihood}
\begin{split}
\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$, respectively.
